Solving an Exam Scheduling Problem Using a Genetic Algorithm

### 2009-11-24 Paper/paper.tex

@@

@@

>>>>

\nocopyright

@@

\begin{abstract}
  This concise, one-paragraph summary should describe the general thesis
  and conclusion of your paper. A reader should be able to learn the purpose
  of the paper and the reason for its importance from the abstract.
\end{abstract}

@@

\section{Conclusion}
  What have you learned because of your project? What can we learn from your
  project? Did it give you ideas as to things you might like to try next?
